**Machine learning identifies unique taxa differentiating proximal and distal

### 2017-05-01 submission/manuscript.Rmd
results tweaked on manuscript

Figure 5:
* 5A: Classifying side of lumen or side of mucosa (L vs R lumen, L vs R mucosa)
* 5B: There are differentially abundant OTUs in right vs left lumen, right vs left mucosa

>>>>

Next, we built a model to differentiate the left and right microbiome. The model performed best when distinguishing the left versus right mucosa (Figure 5A) compared to the left versus right lumen. The model was able to explain ((X%)) of the variance. OTUs that were differentially abundant between the left and right mucosa included members of the _Porphyromonas_, _Murdochiella_, _Finegoldia_, _Anaerococcus_ and _Peptoniphilus_ genera (Figure 5B). The model was less-effective at classifying the right and left lumen ((AUC)). However it did identify differentially abundant OTUs such as three members of the _Bacteroides_ genus, a _Clostridium IV_ OTU and an _Oscillibacter_ OTU (Figure 5C).
